Seismic Hazard Estimation of Northern Iran Using Smoothed Seismicity

### 2017-01-25 abstract.tex
Revision added.

%
This article presents a seismic hazard assessment for northern Iran, where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield good fit with data. We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh, \myrevision{and parts of other neighboring seismic zones that fall within our region of interest. In the chosen approach, seismic events are not assigned to specific faults but assumed to be potential seismogenic sources distributed within regular grid cells. After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes. Seismicity parameters are computed for each seismic zone separately, and for the entire region of interest as a single uniform seismotectonic region. In the analysis we consider uncertainties in the ground motion prediction equation, the seismicity parameters and combine the resulting models using a logic tree.} The results are presented in terms of expected peak ground acceleration (PGA) maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions. \myrevision{According to our results, the highest levels of hazard are observed west of the North Tabriz and east of the North Alborz faults, where expected PGA values are between about 0.5 g and 1 g for 10 and 2 percent probability of exceedance in 50 years, respectively.} We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed. We find our results to be helpful in understanding seismic hazard for northern Iran, \myrevision{but recognize that additional efforts are necessary to obtain more robust estimates at specific areas of interest and different site conditions}.

>>>>

%
This article presents a seismic hazard assessment for northern Iran, where a smoothed seismicity approach has been used in combination with an updated seismic catalog and a ground motion prediction equation recently found to yield good fit with data. We evaluate the hazard over a geographical area including the seismic zones of Azerbaijan, the Alborz Mountain Range, and Kopeh-Dagh, \myrevision{and parts of other neighboring seismic zones that fall within our region of interest. In the chosen approach, seismic events are not assigned to specific faults but assumed to be potential seismogenic sources distributed within regular grid cells. After performing the corresponding magnitude conversions, we decluster both historical and instrumental seismicity catalogs to obtain earthquake rates based on the number of events within each cell, and smooth the results to account for the uncertainty in the spatial distribution of future earthquakes. Seismicity parameters are computed for each seismic zone separately, and for the entire region of interest as a single uniform seismotectonic region. In the analysis we consider uncertainties in the ground motion prediction equation, the seismicity parameters and combine the resulting models using a logic tree.} The results are presented in terms of expected peak ground acceleration (PGA) maps and hazard curves at selected locations, considering exceedance probabilities of 2 and 10 percent in 50 years for rock site conditions. \myrevision{According to our results, the highest levels of hazard are observed west of the North Tabriz and east of the North Alborz faults, where expected PGA values are between about 0.5 g and 1 g for 10 and 2 percent probability of exceedance in 50 years, respectively.} We analyze our results in light of similar estimates available in the literature and offer our perspective on the differences observed. We find our results to be helpful in understanding seismic hazard for northern Iran, \myrevision{but recognize that additional efforts are necessary to obtain more robust estimates at specific areas of interest and different site conditions. \color{red}{A comprehensive study of seismic hazard also needs to include a geological and tectonic features (e.g., faults) of the study area. Although this study results are in a good agreement with studies based on different assumptions, and mostly gives average values due to the smoothing approach, they should not be considered as a final value in seismic design or seismic risk mitigation decisions}}.

### 2017-01-25 conclusions.tex
Revision added.

We present results from a seismic hazard analysis for northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic zonation models. In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model, \myrevision{including uncertainty in the combination of both models, the seismic parameters, and the selection of a ground motion prediction equation via a logic tree approach. In general, our calculations yield results similar to those of other studies for the region of interest and the main cities in it. We, however, provide a newer and alternative perspective to the problem of seismic hazard analysis for norther Iran than previous studies because our use of a more complete seismic catalog, which includes recent damaging events and low-magnitude earthquakes. In our analysis we found that the combination of the regional and uniform models not only allowed us to account for the uncertainty in seismic zonation but it led to a final hazard map that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, the location of known seismically active faults, and the low-magnitude seismic activity in the region}. While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers. Future work to improve the results presented here should consider \myrevision{other ground motion measures of intensity} such as response spectral accelerations for different periods and site effects.

>>>>

We present results from a seismic hazard analysis for northern Iran based on a smoothed seismicity approach, including regional maps of expected peak ground accelerations for different seismic zonation models. In particular, we calculated the hazard for the region of interest using two basic models, a five-seismic zone regions model and a uniform seismic zone model, \myrevision{including uncertainty in the combination of both models, the seismic parameters, and the selection of a ground motion prediction equation via a logic tree approach. In general, our calculations yield results similar to those of other studies for the region of interest and the main cities in it. We, however, provide a newer and alternative perspective to the problem of seismic hazard analysis for norther Iran than previous studies because our use of a more complete seismic catalog, which includes recent damaging events and low-magnitude earthquakes. In our analysis we found that the combination of the regional and uniform models not only allowed us to account for the uncertainty in seismic zonation but it led to a final hazard map that adjusted better to the visual interpretation of the historical and instrumental seismicity observed in the region of interest, the location of known seismically active faults, and the low-magnitude seismic activity in the region}. While no one model can be deemed more appropriate than others, we believe our results constitute a positive contribution to the understanding of seismic hazard in the region, especially for rural areas that are not the subject of specialized hazard studies such as those conducted for major urban centers. Future work to improve the results presented here should consider \myrevision{  \color{red}{generating random fault based on earthquake magnitude as well as considering actual faults}, most recent developed ground motion measures of intensity} such as response spectral accelerations for different periods and site effects.
